### 2015-04-23 Docs/FAQ/faq.tex

\item {\em Does it matter if we use a Fortran 90 compiler instead of a 
   Fortran 95 compiler?}

   On some machines it does---Fortran 95 specifies that any local
   allocated arrays are automatically deallocated when a subroutine
   ends.  Fortran 90 does not do this.  Most \maestro\ routines rely 
   on this Fortran 95 feature.

   On IBM machines, for instance, using {\tt xlf90} instead of {\tt
     xlf95} for \maestro\ will produce memory leaks.

@@

 One implementation of this can be found in {\tt
   AmrPostprocessing/F\_Src/tutorial/fwrite2d.f90}.  This reads in
 the plotfile data using the {\tt plotfile\_module} that the {\tt
   data\_processing} routines rely on, but then builds a multifab
   and writes the data out to a plotfile using the BoxLib write
   routines.

>>>>

\item {\em What version of the Fortran standard is needed?}

  Some features of Fortran 2003 are used, in particular, the {\tt
    ISO_C_BINDING} feature of Fortran 2003 is needed to define a long
  integer type for some MPI operations in Fortran.  This is supported
  by most Fortran compilers even if they don't support the entire
  Fortran 2003 standard.

  We also rely on the Fortran 95 standard that specifies that any
  local allocated arrays are automatically deallocated when a
  subroutine ends.  Fortran 90 does not do this.  Most
  \maestro\ routines rely on this Fortran 95 feature.

@@

 One implementation of this can be found in {\tt
   BoxLib/Tools/Postprocessing/F\_Src/tutorial/fwrite2d.f90}.  This reads in
 the plotfile data using the {\tt plotfile\_module} that the {\tt
   data\_processing} routines rely on, but then builds a multifab
   and writes the data out to a plotfile using the BoxLib write
   routines.
